Response to the defense feedback

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

\begin{equation} \label{chapter:eq:5}
  C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| = \log_2 {|O|}
\end{equation}

@@

\subsubsection{Leakage Detection} 
The access of the address is secret-dependent if $ \exists\, k_{i_1}, k_{i_2} \in K, \, B^{l}_{k_{i_1}} \oplus  B^{l}_{k_{i_2}} =1 $. In the step, we perform the logical exclusive OR operation on every boolearn value in the same address. If the result is $1$, then the address is vulnerable to the side-channel attacks.

>>>>

\begin{equation} \label{chapter:eq:5}
  C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| 
\end{equation}

@@

\subsubsection{Leakage Detection} 
The access of one address is secret-dependent if $ \exists\, k_{i_1}, k_{i_2} \in K, \, B^{l}_{k_{i_1}} \oplus  B^{l}_{k_{i_2}} =1 $. In the step, we perform the logical exclusive OR operation on every boolearn value in the same address. If the result is $1$, then the address is vulnerable to the side-channel attacks.
